Trends of SDR in Thessaloniki

### 2023-06-13 Article_B141.Rmd
Commit 2023-06-13 11:17

output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
# date:           "`r format(Sys.time(), '%F')`"
---

>>>>

output:

  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  word_document:      
    toc:              yes  
  odt_document:       default

# date:           "`r format(Sys.time(), '%F')`"
---
